\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\columnsep}{1cm}
\usepackage{tikz}

\definecolor{linkblue}{HTML}{0066cc}
\definecolor{lightblue}{HTML}{E6F0FA}

\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue
}

\titleformat{\section}{\large\bfseries\uppercase}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{SIDDHARTH T}}\\
    \vspace{4pt}
    \textit{AI \& Machine Learning Engineer} \\
    \vspace{4pt}
    📱 +91 6381857999 \quad ✉️ theprasad@gmail.com \quad
    \href{https://www.linkedin.com/in/sudo-sidd/}{🔗 linkedin.com/in/sudo-sidd} \\
    📍 Coimbatore, Tamil Nadu, India
\end{center}

\vspace{10pt}

\section*{Summary}
A Machine Learning enthusiast with hands-on experience in developing end-to-end AI systems. Skilled in Python, C, and Java with a strong grasp of machine learning tools like PyTorch and OpenCV. Eager to contribute to real-world applications through innovative tech solutions while deepening my expertise in AI/ML domains.

\section*{Education}
\textbf{BTech AIML} \\
Sri Shakthi Institute of Engineering and Technology \\
08/2023 – 05/2027 \quad Coimbatore, Tamil Nadu, India

\section*{Projects}

\subsection*{Image Comparison Tool (Volunteering – AI Prompting Competition)}
Volunteered to build a Python-based evaluation tool for a prompt engineering competition, where participants recreated AI-generated images using text prompts.
\begin{itemize}[noitemsep]
  \item Developed an image comparison system to assess visual similarity between target and recreated images.
  \item Utilized OpenCV, scikit-image, and tkinter for image processing and a user-friendly interface.
  \item \href{https://github.com/sudo-sidd/Image_comparison_application}{GitHub: Image Comparison Tool}
\end{itemize}

\subsection*{Student Attendance System}
Built a classroom attendance tool using low-res face recognition.
\begin{itemize}[noitemsep]
  \item Enabled teachers to upload images for hourly student attendance tracking.
  \item Developed a face recognition module to identify multiple students simultaneously.
  \item \href{https://github.com/SaiDinakar/Student-Attendance}{GitHub: Attendance System}
\end{itemize}

\subsection*{Gallery Management Application (Face Recognition Admin Panel)}
Web-based system using FastAPI to support face recognition model pipelines.
\begin{itemize}[noitemsep]
  \item Created admin interface to manage face galleries, student records, and model files.
  \item Streamlined training and deployment workflows.
  \item \href{https://github.com/sudo-sidd/Face_Gallery-Manager}{GitHub: Gallery Manager}
\end{itemize}

\subsection*{Face Data Collection App}
Developed a video-based data collection tool for face dataset generation.
\begin{itemize}[noitemsep]
  \item Enabled students to record high-res video and auto-extract frames for training.
  \item Integrated with gallery management system for streamlined data ingestion.
  \item \href{https://github.com/sudo-sidd/Face_Data_Collection-System}{GitHub: Data Collection App}
\end{itemize}

\subsection*{Corrugated Box CRM Application}
Built CRM using Django and Electron for manufacturing clients.
\begin{itemize}[noitemsep]
  \item Integrated customer management, order tracking, and reporting.
  \item Desktop deployment using Electron for offline capabilities.
\end{itemize}

\section*{Key Achievements}
\begin{itemize}[noitemsep]
  \item \textbf{Student Attendance Accuracy:} Achieved 95\% face recognition accuracy.
  \item \textbf{CRM Enhancement:} Increased sales tracking efficiency by 20\%.
  \item \textbf{Prompting Contest Evaluation:} Delivered 90\% image comparison accuracy.
\end{itemize}

\section*{Tools and Frameworks}

\textbf{Programming Languages} \\
\colorbox{lightblue}{Python} \quad
\colorbox{lightblue}{C} \quad
\colorbox{lightblue}{Java} \quad
\colorbox{lightblue}{JavaScript}

\vspace{6pt}

\textbf{ML \& Data Libraries} \\
\colorbox{lightblue}{PyTorch} \quad
\colorbox{lightblue}{Torchvision} \quad
\colorbox{lightblue}{Pandas} \quad
\colorbox{lightblue}{Numpy} \quad
\colorbox{lightblue}{OpenCV}

\vspace{6pt}

\textbf{Frameworks \& Dev Tools} \\
\colorbox{lightblue}{Django} \quad
\colorbox{lightblue}{Electron} \quad
\colorbox{lightblue}{Node.js} \quad
\colorbox{lightblue}{VSCode} \quad
\colorbox{lightblue}{Git} \quad
\colorbox{lightblue}{GitHub}

\section*{Languages}
\textbf{English:} Proficient \quad ●●●○○ \\
\textbf{Tamil:} Native \quad ●●●●●

\section*{Strengths}
\begin{itemize}[noitemsep]
  \item \textbf{Problem-solving:} Able to break down complex issues and deliver optimized solutions.
  \item \textbf{Creative Thinking:} Delivers intuitive and user-friendly designs for technical challenges.
  \item \textbf{Adaptability:} Quickly learns and thrives in fast-paced environments.
\end{itemize}

\end{document}
